Project 1 Checkpoint

### 2015-02-05 project1/checkpoint/main.tex
Adding a README

\section{Current Build}
Current Build

\cite{cts12}
\bibliographystyle{plain}
\bibliography{main}

>>>>

\section{Current Build}
The simulation is currently deployed at \cite{aprilandchip} and currently runs a fixed number of cars through stepping
at 1 second real time being equal to 100ms. Eventually, this will be adjustable in real-time, and better visualized.

To build the application locally, you'll need to install a version of node at 0.10.0 or higher. This will be bundled
with npm. Since this project uses gulp for a task runner, you'll need to install it globally via
\texttt{npm install -g gulp}. Inside the \texttt{simulation} directory, you'll need to pull in packages with just
\texttt{npm install}. Once that installs, running \texttt{gulp} will run the build for you and generate a
\texttt{main.js} that's included in the \texttt{index.html} file. Opening this file in a browser should run the
simulation.

\bibliographystyle{plain}
\bibliography{main}
